---
title: "STAT 385 Learning Progress"
author: "Bradley Simon"
date: '2020-03-04'
output: html_document
slug: stat-385-learning-progress
tags: r
categories: blog
---
The first topics I learned in R were basic mathematical operations, creating functions, data types, data structures, and data frames. One of the first functions I created was a French Roulette wheel that returns whether the user's input bet wins or not. The code for this function is shown below.



```{r}
wheel <- read.csv("https://nkha149.github.io/stat385-sp2020/files/data/roulette.csv")
roulette <- function(bet = 14) {
  win_num <- sample(x = 1:37, size = 1)
  wheel[win_num, 1] == bet
}
set.seed(385)
roulette(bet = 10)
```



I have also learned how to modify vlaues in lists, vectors, matrices, and data frames, as well as how to graph data sets. The code for a scatterplot that is categroized by color is shown below.



```{r}
plot(formula = Sepal.Width ~ Sepal.Length, data = iris,
     col = c("green", "red", "blue")[iris$Species],
     main = "Iris Sepal Length vs. Sepal Width by Species",
     xlab = "Sepal Length", ylab = "Sepal Width", pch = 16)
grid()
```



Lastly, I have learned how to utilize parellel computing by vectorizing functions. I took the loop function shown below and vectorized it so that the speed was increased significantly.



```{r}
roulette_loop <- function(many_bets) {
  win_lose_random <- sample(x = c(TRUE, FALSE), size = length(many_bets),
                            replace = TRUE)
  total_prize <- c()
  for (i in 1:length(many_bets)) {
    bet <- many_bets[i]
    prize <- 0
    if (win_lose_random[i]) {
      if (bet == 'low') {
        prize <- 10
      } else if (bet == 'high'){
        prize <- 10
      } else if (bet == 'red') {
        prize <- 20
      } else if (bet == "black") {
        prize <- 20
      } else if (bet == "odd") {
        prize <- 15
      } else if (bet == "even") {
        prize <- 15
      } else if (bet == "first") {
        prize <- 50
      } else if (bet == "second") {
        prize <- 50
      } else if (bet == "third") {
        prize <- 50
      }
    }
  total_prize <- c(total_prize, prize)
  }
  
  total_prize
}
set.seed(385)
long_vec <- rep(c("red", "black", "low", "high", "second", "first", "third",
                  "odd", "even"), 10000)
system.time(roulette_loop(many_bets = long_vec))
```

```{r}
roulette_vec <- function(many_bets){
  win_lose_random <- sample(x = c(TRUE, FALSE), size = length(many_bets),
                            replace = TRUE)
  look_up_table <- c("low" = 10,"high" = 10, "red" = 20, "black" = 20, "odd" =   15,"even" = 15,
                     "first" = 50, "second" = 50, "third" = 50)
  prize <- look_up_table[many_bets]
  unname(win_lose_random * prize)
}


set.seed(385)
long_vec <- rep(c("red", "black", "low", "high", "second", "first", "third",
                  "odd", "even"), 10000)
system.time(roulette_vec(many_bets = long_vec))
```

