---
title: "Bollywood Filmfare Awards"
author: "Bradley Simon"
date: "2020-04-27"
output: html_document
---

```{r}
CWLData <- read.csv("https://raw.githubusercontent.com/brsimon2/Bollywood_Filmfare/master/Filmfare-Awards.csv")
```

# Graph 1

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(scales)
Box_Office_IMDBRating <- CWLData %>% 
  group_by(IMDB.rating) %>% 
  summarise(Total_Box_Office = sum(as.numeric(Box.Office.Earnings.in.Rupees), na.rm = TRUE))

ggplot(data = Box_Office_IMDBRating, mapping = aes(x = IMDB.rating, y = Total_Box_Office)) +
  geom_smooth(color = "dodgerblue") +
  labs(x = "IMDB Rating", y = "Box Office Earnings in Rupees")+
  scale_y_continuous(labels = comma)
```

**This graph shows that a higher IMDB rating does not necesssarily relate to more box office earnings.**

# Graph 2

```{r}
Box_Office_Month <- CWLData %>% 
  select(Release.month,Box.Office.Earnings.in.Rupees) %>% 
  filter(!is.na(Box.Office.Earnings.in.Rupees)) %>% 
  group_by(Release.month) %>% 
  summarise(Total_Box_Office = mean(as.numeric(Box.Office.Earnings.in.Rupees), na.rm = TRUE))

ggplot(data = Box_Office_Month, mapping = aes(x = Release.month, y = Total_Box_Office)) +
  geom_bar(fill = "darkgreen", stat = "identity") +
  labs(x = "Release Month", y = "Average Box Office Earnings in Rupees")+
  coord_flip()+
  scale_y_continuous(labels = comma)
```

**From the graph, it is clear that movies released in May have a higher likelihood of receive higher box office earnings.**

# Graph 3

```{r}
Filtered_CWLData <- CWLData %>% 
  filter(!is.na(Box.Office.Earnings.in.Rupees))

ggplot(data = Filtered_CWLData, mapping = aes(x = Release.month)) +
  geom_bar(fill = "darkorange") +
  labs(x = "Release Month")+
  coord_flip()+
  labs(y = "Total Movies Released", x = "Month")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10))
```

**Most award winning movies are released in January and December.**

# Graph 4
```{r}
Director_Earnings <- Filtered_CWLData %>% 
  group_by(Directors) %>% 
  summarise(Total_Box_Office = sum(as.numeric(Box.Office.Earnings.in.Rupees), na.rm = TRUE)) %>% 
  arrange(desc(Total_Box_Office)) %>% 
  head(n=8)


ggplot(data = Director_Earnings, mapping = aes(x = Directors, y = Total_Box_Office)) +
  geom_bar(fill = "red", stat = "identity") +
  labs(x = "Producer", y = "Box Office Earnings in Rupees")+
  coord_flip()+
  scale_y_continuous(labels = comma)
```

**Among the award winning movies, Aamir Khan, Kiran Rao, & Siddharth Roy Kapoor directed the movies with the most box office earnings together.**

# Graph 5
```{r}
ggplot(data = Filtered_CWLData, mapping = aes(x = Year, y = Box.Office.Earnings.in.Rupees)) +
  geom_area(fill = "purple") +
  labs(x = "Year", y = "Box Office Earnings in Rupees")+
  scale_y_continuous(labels = comma)+
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10))
```

**It appears that box office earnings increased over time, most likely due to inflation. 1990, 2010, and 2017 were years that had especially high box office earnings.**
